\documentclass[a4paper,11pt]{letter}

%\usepackage{latexsym}
\usepackage{caption2}
%\usepackage{graphicx}
%\usepackage{natbib}
\usepackage[latin1]{inputenc}
\usepackage{color}
\usepackage{array}
%\usepackage{longtable}
%\usepackage{calc}
%\usepackage{multirow}
%\usepackage{hhline}
%\usepackage{ifthen}
%\usepackage{lscape}

\oddsidemargin 1cm

\topmargin 0.75cm 
\textwidth 16cm

\textheight 22cm

\pagestyle{empty}

\begin{document}
\vspace{-6 in}

To Search committee\\
National Center for Ecological Analysis and Synthesis\\
735 State St. Suite 300\\
Santa Barbara, California\\
93101, USA.
\\
\\
Dear Committee:\\
\vspace{0.05 in}

Please consider my application for the quantitative analyst/scientific
programmer/internet technologist at the National Center for Ecological
Analysis and Synthesis to support the development of new scientific
applications for the Ocean Health Index.

My interest in doing synthesis linking large data sets and theory in
ecology and evolution to understand the origin and coexistence of
biodiversity began while I studied Biology and Environmental Sciences
from 1995-1998 in Madrid, Spain. Through several undergraduate
research projects, I became interested in the Ecology and Evolution of
Ecosystems and began working on my PhD. with Dr. Jordi Bascompte at
the Do\~nana Biological Station, Seville, Spain. I completed my
PhD. in 2005 on ``The Structure and Dynamics of Ecological Networks.''

I have been a postdoctoral fellow at the National Center for
Ecological Analysis and Synthesis (NCEAS) at University of California
in Santa Barbara since February 2005. I am particularly interested in
a position who seek the development and implementation of efficient
and appropriate computational and analytical solutions to integrate
approaches that bridge disciplines and span multiple levels of
biological organization. As you may note from my CV I have been
developing and testing novel stochastic models using large data sets
from a variety of sources.

Computing staff at NCEAS has definitively influenced me in the following ways:
\begin{itemize}
\item Fostering my research in the context of open software,
  management of large data sets, development of new models-methods and
  thinking in interdisciplinary research.
\item Developing new theories in ecological networks that attempt to
  scale up from individuals to ecosystems.
\item Participation in different teaching programs that attempt to
  develop strategies for education in ecology and evolution, diversity
  and sustainability.
\item Collaboration with several researchers from other institutions
worldwide.
\end{itemize}
\\
I have enclosed my resume.
\\
Sincerely Yours,
\\
\\
Carlos J. Meli\'an,\hspace{1.75 in}  Santa Barbara, January 29, 2010.\\
Phone: (805) 892 2527\\
e-mail: melian@nceas.ucsb.edu\\
http://www.nceas.ucsb.edu/$\sim$ melian/\\
\end{document}
